\newcommand{\pdfglyphtounicode}[2]{}
\newcommand{\chref}[2]{\smash{\textcolor{blue}{\href{#1}{#2}}}}

\documentclass[letterpaper, 10pt]{article}

\usepackage{etoolbox}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}

% Set underlining to be closer to text
\setul{1pt}{.4pt}

% Set the margins to be .5 inches
\usepackage[margin=0.5in]{geometry}


% Make URLs appear as if they weren't URLs
% (i.e. not blue and underlined)
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%  \pdfgentounicode=1

\begin{document}
% Load in the custom resume commands
\include{utils}

\begin{center}
	\textbf{\Huge \scshape \href{https://404wolf.com}{Wolf Mermelstein}} \\ \vspace{4pt}

	\href{https://404wolf.com}{www.404Wolf.com}
	$\cdot$
	\small \href{tel:(+12127679653)}{(212)767-WOLF}
	$\cdot$
	\href{mailto:wolf.mermelstein@case.edu}{wolf.mermelstein@case.edu}
	$\cdot$
	\href{https://linkedin.com/in/wolfmermelstein}{linkedin.com/in/wolfmermelstein}
	$\cdot$
	\href{https://github.com/404wolf}{github.com/404Wolf}
\end{center}
\vspace{-16px}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheadingCompact
{Case Western Reserve University}{Cleveland, OH}
{B.S. Computer Science; 4.00 GPA}{Anticipated 2026}{\textbf{Relevant courses:} Data Structures, Linux Tools/Scripting; Taking Networks, Algo, OS, Corporate Finance}{\textbf{Experience:} \href{https://case.edu/entrepreneurship/fellowships/veale-snyder-fellows-program}{\textcolor{blue}{Veale Snyder Fellow} (entrepreneurship program)}, Board Game Club VP, former IT working group}

\vspace{3.5pt}

\resumeSubheadingCompact
{Bard Early College}{Queens, NY}
{Associates of Arts;  4.00 GPA}{Sep. 2021 - June 2023}{}{}
\resumeSubHeadingListEnd

\section{Awards \& Honors}
\resumeSubHeadingListStart

\resumeSubItem[]{HackCWRU (University Hackathon) First Place}{\rightInfo{February 2024}}
\resumeSubItem[]{Case Western ThinkBox Student Project Fund (\$630)}{\rightInfo{October 2023}}
\resumeSubItem[]{Bard High School Early College Departmental Nanoscience and Ancient Latin awards}{\rightInfo{May 2023}}
\resumeSubItem[]{Microsoft Bug Hunter Acknowledgment}{\rightInfo{March 2022}}
\resumeSubItem[]{Hackett Certificate for ``greatest proficiency in oratory, either verse or prose''}{\rightInfo{May 2022}}

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Recurse Center}{Brooklyn-based self-led coding retreat}{June 2023 - August 2023; June 2024 - August 2024; NYC \& Remote}
{Participant}{}{}
\resumeItemListStart
\resumeItem{Personal Website \tinyblue{(\href{https://404wolf.com}{site}, \href{https://github.com/404wolf/404wolf.com}{code})}}
{Designed website with TS/TSX, React, \& tailwind. Implemented custom post editing system with Postgres/Prisma-ORM \& S3 to store/fetch/render posts (w/REST CRUD). Wrote (TS) backup and migration scripts. Created special markdown parsing system with custom Rehype plugins. Wrote Obsidian plugin to sync/edit blogs.}

\resumeItem{NixOS \& Nix Builds}
{Contributed to \href{https://github.com/NixOS/nixpkgs}{nixpkgs}. Configured NixOS desktop system from scratch w/Hyprland, home-manager, and other extensive customizations. Learned Nix language/packaging binaries \& various programs. Working on project to dockerize Android emulators with Nix docker tools \tinyblue{\href{https://github.com/404Wolf/android-docker}{(code)}}.}

\resumeItem{Generated Vocab Cards \tinyblue{\href{https://github.com/orgs/Logophilio/repositories}{(code)}}}
{Created Python Django server to merge Webster, OpenAI, and other API data into elegant English Vocab flashcard PDFs. Made system to generate vector art using template SVGs and Chrome Devtools Protocol.}
\resumeItemListEnd

\resumeSubheading
{Brooklyn Robot Foundry}{Robotics afterschool \& summer camp franchise}{July 2020 - June 2023; NYC \& Remote}
{Design Team; Teacher}{}{}

\resumeItemListStart
\resumeItem{Design system overhaul}
{Crafted dynamic presentation templates and inventory management systems for designers \& teachers, improving robot kit creation process. Educated staff on using the materials.}

\resumeItem{Curriculum Design \& Teaching}
{Developed novel `inventors' curriculum fostering open-ended exploration with 40+ unique lessons, taught to 10-12 year olds throughout the country \& created content for astronomy `Science Lab' course w/thorough, interactive lessons for 6-9 yr olds. Taught classes, including my curricula, to groups of 5-12 8-13 year olds.}
\resumeItemListEnd

\resumeSubheading
{Minecraft Name Autoclaiming \tinyblue{\href{https://github.com/404wolf/ember}{(code)}}}{Online self-run business}{June 2021 - July 2022; Remote}
{Co-founder; Solo Software Engineer; Sales Manager}{}{}
\resumeItemListStart
\resumeItem{Software Engineer}
{Developed system w/Python to autoclaim desirable Minecraft usernames at moment of release. Automated server deployment and account distribution for 50-80 accounts. Implemented automatic name queue, server-setup scripts, AioHTTP Swagger-Spec'ed management server, and admin interface. Utilized Vultr API for server deployment and AsyncSSH for auth \& SFTP.}

\resumeItem{Sales Management}
{Facilitated sales process and auctions for over 100 buyers, generating \$6,000+ in revenue with around 200 unique accounts sold. Maintained consistently positive customer feedback and regular reorders.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-16pt}

\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{DNA Nanotube Designer Tool (``NATuG'') (\chref{https://404wolf.com/posts/project/DNANanotubes}{blog}, \chref{https://wolf-mermelstein-personal-website.s3.us-east-2.amazonaws.com/programOverview_0001_0001_0001.webm}{demo}, \chref{https://github.com/NATuG3/NATuG3}{code})}
{DNA nanotechnology academic research project. Developed interactive PY-QT desktop app to streamline geometrically constrained DNA nanotube design. Collaborated w/bionanotechnologist to create important algorithms like determining helix strand switch behavior on junction clicks. Designed export file format. Wrote manual and Began working on scholarly paper.}

\resumeSubItem{Coin Sorting Bot (\chref{https://404wolf.com/posts/project/coinSortBot}{blog}, \chref{https://github.com/orgs/Coin-Sort-Bot/repositories}{code})}{Robot to sort coins by date. 3D printed body with mechanism that sends coins down chute to photo them and deflect into canisters. Django/S3 backend for processing.}

\resumeSubItem{Android in the Browser (\chref{https://404wolf.com/posts/project/androidBrowser}{blog}, \chref{https://github.com/404Wolf/Browser-Phone}{code})}
{Developed toolchain to stream Android to browsers over WebRTC w/Janus Gateway for low-latency video stream. Using Nix for Android packaging, React for frontend, Bun for APIs, and Android development tools. Goal is interactive Android in browser w/simple React components.}

\resumeSubItem{CWRU Food Finder (\chref{https://404wolf.com/posts/project/freeCwruFood}{blog}, \chref{https://free-cwru-food.404wolf.com/}{demo}, \chref{https://free-cwru-food.404wolf.com/}{code})}
{Website using fine-tuned OpenAI model w/Google Cloud Run \& MongoDB automated workflow to scrape on-campus events \& categorize by free food. Includes MUI/React/NextJS frontend. Uses puppeteer to scrape additional event details. 2023 1\textsuperscript{st} place university hackathon project. About 50 visitors/month.}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Fluent English \& Ancient Latin learner. Python, Typescript, Javascript, Java, Bash, Nix, HTML \& CSS, Markdown \& \LaTeX, Typst, Lua, Awk, learning Verilog, learning C/C++}

\resumeSubItem{Tools}{Nix \& NixOS, Linux, Docker, NextJS \& NextAuth, Numpy \& Pandas, Prisma, Django, PyQt \& PyQtGraph, Asyncio, Unified/Remark \& Rehype, Git, S3, AWS, Fusion 360, Janus Gateway \& WebRTC, React/React Native, Tailwind, Mui, Adobe Illustrator \& Photoshop, GSuit \& MS Office, Vim, JQ, CLI tooling}

\resumeSubItem{Miscellaneous}{Object-oriented, functional, Web development, 110+ WPM Typing, CPR Certified (2022). Fast learner, creative, good communicator.}

\resumeSubHeadingListEnd

\begin{picture}(0,0)
	\put(7.82in, -0.29in){\makebox(0,0)[rb]{
    \fontsize{5pt}{5pt}\selectfont \href{https://github.com/404wolf/resume}{Built with Nix; \textcolor{blue}{Source on GitHub}}
}}
\end{picture}

\end{document}

\end{document}

